Clustering exploration for `r params$library_id`

### 2024-11-20 analyses/cell-type-ewings/template_notebooks/clustering-workflow/01-clustering-metrics.Rmd
add parameters as actual parameters

---
title: "Clustering exploration for `r params$library_id`"
author: Ally Hawkins
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_depth: 3
    code_folding: "hide"
params:
  library_id: "SCPCL000822"
  sce_file: "../../../../data/current/SCPCP000015/SCPCS000490/SCPCL000822_processed.rds"
  cluster_results_file: "SCPCL000822_clusters.tsv"
---

@@

- Nearest neighbors: 5, 10, 15, 20, 25, 30, 35, and 40
- Resolution: 0.5, 1, 1.5

Leiden clusters are calcualted using the following range of parameters:

- Objective function: CPM and modularity 
- Nearest neighbors: 5, 10, 15, 20, 25, 30, 35, and 40
- Resolution: 0.5, 1, 1.5

@@

```{r}
# louvain clustering across all parameters 
louvain_results <- rOpenScPCA::sweep_clusters(
  sce,
  algorithm = "louvain",
  nn = seq(5, 40, 5),
  resolution = c(0.5, 1, 1.5)
) |> 
  dplyr::bind_rows() |> 
  # add in objective function so we can combine with leiden results
  dplyr::mutate(objective_function = NA_character_)

# leiden cpm clustering
leiden_cpm_results <- rOpenScPCA::sweep_clusters(
  sce,
  algorithm = "leiden",
  nn = seq(5, 40, 5),
  resolution = c(0.001, .005, .01),
  objective_function = "CPM"
) |> 
  dplyr::bind_rows()

# leiden modularity clustering
leiden_mod_results <- rOpenScPCA::sweep_clusters(
  sce,
  algorithm = "leiden",
  nn = seq(5, 40, 5),
  resolution = c(0.5, 1, 1.5),
  objective_function = "modularity"
) |> 
  dplyr::bind_rows()
```

>>>>

---
title: "Clustering exploration for `r params$library_id`"
author: Ally Hawkins
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_depth: 3
    code_folding: "hide"
params:
  library_id: "SCPCL000822"
  sce_file: "../../../../data/2024-07-08/SCPCP000015/SCPCS000490/SCPCL000822_processed.rds"
  cluster_results_file: "SCPCL000822_clusters.tsv"
  nn_range: !r seq(5, 40, 5)
  louvain_res_range: !r c(0.5, 1, 1.5)
  mod_res_range: !r c(0.5, 1, 1.5)
  cpm_res_range: !r c(0.001, 0.005, 0.01)
---

@@

- Nearest neighbors: `r paste0(params$nn_range, collapse = ", ")`
- Resolution:`r paste0(params$louvain_res_range, collapse = ", ")`

Leiden clusters are calculated using modularity as the objective function with the following range of parameters:

- Objective function: modularity 
- Nearest neighbors: `r paste0(params$nn_range, collapse = ", ")`
- Resolution: `r paste0(params$mod_res_range, collapse = ", ")`

Leiden clusters are calculated using CPM as the objective function with the following range of parameters:

- Objective function: CPM 
- Nearest neighbors: `r paste0(params$nn_range, collapse = ", ")`
- Resolution: `r paste0(params$cpm_res_range, collapse = ", ")`

@@

```{r}
# louvain clustering across all parameters 
louvain_results <- rOpenScPCA::sweep_clusters(
  sce,
  algorithm = "louvain",
  nn = params$nn_range,
  resolution = params$louvain_res_range
) |> 
  dplyr::bind_rows() |> 
  # add in objective function so we can combine with leiden results
  dplyr::mutate(objective_function = NA_character_)

# leiden cpm clustering
leiden_cpm_results <- rOpenScPCA::sweep_clusters(
  sce,
  algorithm = "leiden",
  nn = params$nn_range,
  resolution = params$cpm_res_range,
  objective_function = "CPM"
) |> 
  dplyr::bind_rows()

# leiden modularity clustering
leiden_mod_results <- rOpenScPCA::sweep_clusters(
  sce,
  algorithm = "leiden",
  nn = params$nn_range,
  resolution = params$mod_res_range,
  objective_function = "modularity"
) |> 
  dplyr::bind_rows()
```
